Abstract

### 2025-03-02 output/Letter_to_editor_reviewers.Rmd
Add remark about implicit canonical basis in model

> Third, as responses are not necessarily interpreted as correct or incorrect,
parameter $`r INTERCEPT_PARAM`$ is said to be related to the item _location_
instead of the item difficulty.
Finally, it is worth noting that
this formulation assumes *within-item multidimensionality* in general,
which will be present whenever more than one component of $`r DISCR_VECTOR`$
is non-null.
However, the model can also account for *between-item multidimensionality*,
if all items are unidimensional
(i.e., their $`r DISCR_VECTOR`$ parameters only have one non-null component).

>>>>

> [...] Finally, it is worth noting that
this formulation assumes *within-item multidimensionality* in general,
which will be present whenever more than one component of $`r DISCR_VECTOR`$
is non-null.
However, the model can also account for *between-item multidimensionality*,
if all items are unidimensional
(i.e., their $`r DISCR_VECTOR`$ parameters only have one non-null component).

### 2025-03-02 output/Main_text.Rmd
Add remark about implicit canonical basis in model

We must stop here and make a few remarks. First, as we are not constraining
ourselves to cognitive traits,
we speak of _positive_ instead of _correct response_. This may imply giving
a correct response indeed, if we are talking about a cognitive test.
But it may mean endorsing an item (or a certain response option)
in a non-cognitive domain.
Second, although not explicitly stated, $`r DISCR_VECTOR`$ is a vector of
non-negative real numbers in @reckase_difficulty_1985
---a decrease in the probability of a correct response
with an increase in ability makes little sense.
In our case, $`r DISCR_VECTOR`$ is a vector of real numbers; the value
of the $`r DIM_INDEX`$-th component $`r DISCR_PARAM`$ can be negative if
the item is negatively-keyed for latent dimension $`r DIM_INDEX`$.
Third, as responses are not necessarily interpreted as correct or incorrect,
parameter $`r INTERCEPT_PARAM`$ is said to be related to the item _location_
instead of the item difficulty.
Finally, it is worth highlighting that
this model generally assumes *within-item multidimensionality*,
which will be present whenever more than one component of $`r DISCR_VECTOR`$
is non-null.
However, the model can also account for *between-item multidimensionality*,
if the $`r DISCR_VECTOR`$ parameter only has one non-null component.

>>>>

We must stop here and make a few remarks. First, as we are not constraining
ourselves to cognitive traits,
we speak of _positive_ instead of _correct response_. This may imply giving
a correct response indeed, if we are talking about a cognitive test.
But it may mean endorsing an item (or a certain response option)
in a non-cognitive domain.
Second, as responses are not necessarily interpreted as correct or incorrect,
parameter $`r INTERCEPT_PARAM`$ is said to be related to the item _location_
instead of the item difficulty.
Third, although not explicitly stated, $`r DISCR_VECTOR`$ is a vector of
non-negative real numbers in @reckase_difficulty_1985
---a decrease in the probability of a correct response
with an increase in ability makes little sense.
In our case, $`r DISCR_VECTOR`$ is a vector of real numbers; the value
of the $`r DIM_INDEX`$-th component $`r DISCR_PARAM`$ can be negative if
the item is negatively-keyed for latent dimension $`r DIM_INDEX`$.
Fourth, $`r DISCR_VECTOR`$ is expressed on an algebraic basis,
which the MIRT literature implicitly assumes to be the canonical basis
(we will show that this assumption is not necessary though).
Finally, it is worth highlighting that
this model generally assumes *within-item multidimensionality*,
which will be present whenever more than one component of $`r DISCR_VECTOR`$
is non-null.
However, the model can also account for *between-item multidimensionality*,
if the $`r DISCR_VECTOR`$ parameter only has one non-null component.
